---
title: "Tp1 PART TWO :"
output: html_document
date: "2024-02-28"

---
## CHAIMA TALHI M1-CS
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# EXO 1 :
## Simple regression application
### Step 1: 

#### Load the data into a variable named "tab"

```{r}
 
tab <- read.table("~/Desktop/chaimas2/ml/R/Data(1)/Data/DataHeight.txt", header = TRUE)

```

### Step 2: 

#### Load the vector "age" into a variable named "x"

```{r}
x <- tab$age
```

### Step 3: 

#### Load the vector "height" into a variable named "y"

```{r}
y <- tab$height
```

### Step 4: 

#### Plot the distribution of y with respect to x
```{r}

#the functions plot() and qplot() are used for creating plots and visualizations. 
#plot() is a generic function in R that can create various types of plots depending on the object provided.
#qplot() is a function from the ggplot2 package, which is a powerful and popular package for creating visually appealing and customizable plots.

plot(x, y, xlab = "Age", ylab = "Height", main = "Distribution of Height by Age")


```

### Step 5: 

#### Based on the graph : there is a positive correlation between the two variables height and the age, so when the age increases, height increases . 


### Step 6: 

#### Perform a statistical test to determine the correlation between x and y
```{r}
cor_test <- cor.test(x,y)
print(cor_test)

```

### Step 7: 

#### Get the parameter values (q0 and q1)
```{r}
q1 <- cor_test$estimate
q0 <- mean(y) - q1 * mean(x)

```

### Step 8: 

#### Calculate the residual error
```{r}
residuals <- y - (q0 + q1 * x)  # y-y_hat  
residual_error <- sum(residuals^2) # this is the function cost 

```


### Step 9: 

#### Equation of the regression line
```{r}
regression_equation <- paste("Height =", round(q0, 2), "+", round(q1, 2), " * Age")

```


### Step 10: 

#### Plot the regression line
```{r}
#The abline() function in R is used to add a straight line to a plot. 
#its main goal is to draw a regression line on a scatter plot or any other plot where a straight line is desired.
plot(x, y, xlab = "Age", ylab = "Height", main = "Distribution of Height by Age")
abline(q0, q1, col = "red")

```
 

### Step 11: 

#### Predict the heights of 4 children with ages 3, 7, 9, and 12
```{r}
new_age <- c(3,7,9,12)
predicted_heights <- q0 + q1 * new_age
print(predicted_heights)
```


### Step 12: 

#### Predict the height of a 10-year-old child with a 95% confidence interval
```{r}
model <- lm(height ~ age, data = tab)
new_age <- 10
predicted_height <- q0 + q1 * new_age

# Create a new data frame with the desired age
new_data <- data.frame(age = new_age)

# Calculate the confidence interval
confidence_interval <- predict(model, newdata = new_data, interval = "confidence", level = 0.95)

print(predicted_height)
print(confidence_interval)


```



# EXO 2 :
## Multiple & Polynomial Regression

```{r}
#Reads the data from a file and assigns it to the variable LungCapData.
LungCapData <- read.table("~/Desktop/chaimas2/ml/R/Data(1)/Data/LungCapData.txt", header = T, sep="\t")

#Attaches the data frame, allowing direct access to its variables without specifying the data frame name. 
attach(LungCapData)

#Retrieves the names of the variables in the data frame.
names(LungCapData)

#Determines the class (data type) of the Age and Smoke variables.
class(Age)
class(Smoke)

#Determines the levels (categories) of the Smoke variable.
levels(Smoke)

#Constructs a linear regression model (model1) to predict 
#lung capacity (LungCap) based on age (Age) and height (Height).
model1 <- lm(LungCap ~ Age + Height)

#provide a summary 
summary(model1)

#computes the Pearson correlation coefficient between the Age and Height variables.
cor(Age, Height, method="pearson")

#Computes the confidence intervals for the coefficients in model1 at a 95% confidence level.
confint(model1, coef.level=0.95)

#Constructs a multiple linear regression model
model2 <- lm(LungCap ~ Age + Height + Smoke + Gender + Caesarean)

#Provides a summary of the model2 regression model
summary(model2)
plot(model2)


```




