---

---
# CHAIMA TALHI CS
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# TP 3 : PART ONE

## EXO 1 :

# with rpart

#### Load the rpart library on R :

```{r}
install.packages("rpart")
library(rpart)

```


#### Create the simplified tennis dataset :

```{r}
tennis <- data.frame(
  Outlook = c("Sunny", "Sunny", "Overcast", "Rainy", "Rainy", "Rainy", "Overcast", "Sunny", "Sunny", "Rainy", "Sunny", "Overcast", "Overcast", "Rainy"),
  Temperature = c("Hot", "Hot", "Hot", "Mild", "Cool", "Cool", "Cool", "Mild", "Cool", "Mild", "Mild", "Mild", "Hot", "Mild"),
  Humidity = c("High", "High", "High", "High", "Normal", "Normal", "Normal", "High", "Normal", "Normal", "Normal", "High", "Normal", "High"),
  Wind = c("Weak", "Strong", "Weak", "Weak", "Weak", "Strong", "Strong", "Weak", "Weak", "Weak", "Strong", "Strong", "Weak", "Strong"),
  Play = c("No", "No", "Yes", "Yes", "Yes", "No", "Yes", "No", "Yes", "Yes", "Yes", "Yes", "Yes", "No")
)

```


#### Display the structure of the dataset :

```{r}
str(tennis)

```

#### Create decision trees with different minimal node sizes :

```{r}
tree_minsplit_1 <- rpart(Play ~ . , data = tennis , minsplit = 1)
tree_minsplit_2 <- rpart(Play ~ ., data = tennis, minsplit = 2)
tree_minsplit_5 <- rpart(Play ~ ., data = tennis, minsplit = 5)
tree_minsplit_14 <-rpart(Play ~ ., data = tennis, minsplit = 14)
```

#### Visualize the trees :

```{r}

plot(tree_minsplit_1)
text(tree_minsplit_1)
plot(tree_minsplit_2)
text(tree_minsplit_2)
plot(tree_minsplit_5)
text(tree_minsplit_5)
plot(tree_minsplit_14)
text(tree_minsplit_14)
```
 

## EXO 2 :

# with tree

#### Load the iris dataset  :

```{r}

data(iris)

```

#### Display the first few records   :

```{r}

head(iris)

```

#### Load the rpart library  :

```{r}

library(rpart)

```

#### Create decision trees:

```{r}
tree <- rpart(Species ~ ., data = iris)

#Visualize the decision tree

plot(tree)
text(tree)

```

#### Evaluate the classification quality :
### Predict the species using the decision tree
```{r}

predicted <- predict(tree, newdata = iris, type = "class")

```


# Create a confusion matrix
```{r}

table(iris$Species, predicted)

```

## EXO 3 :

#  with C5.0 :

#### Load the c50 package on R :

```{r}

library(rpart)
library(gmodels)

```


#### load the file  credit.csv :

```{r}
credit <- read.csv('~/Desktop/chaimas2/ml/TALHI-CHAIMA-CS-M1/credit.csv')

```

#### print the header of the file credit.csv :

```{r}

head(credit)
```

#### print the structure  :

```{r}

str(credit)
```


#### display the number of occurances of checking balance and savings balance  :

```{r}

table(credit$checking_balance)
table(credit$savings_balance)

```



#### display the statistics of months_loan_duration  :

```{r}

summary(credit$months_loan_duration)


```

#### display the statistics of amount  :
```{r}

summary(credit$amount)


```

#### display the props of credit result   :
```{r}

prop.table(table(credit$default))


```


#### Répartir les données credit.csv en 90% pour l'apprentissage et 10% pour les tests  :
```{r}

set.seed(123) # To make the splitting reproducible
train_indices <- sample(1:nrow (credit) ,0.9*nrow(credit))
train_data <- credit[train_indices, ]
test_data <- credit[-train_indices, ]

```




#### Vérifier les proportions par la commande prop.table :
```{r}

prop.table(table(train_data$default))
prop.table(table(test_data$default))

```



####  Créer un modèle d'arbre de décision par rpart :
```{r}

model <- rpart(default  ~ ., data = train_data)

```


####  evaluation du model :
```{r}

summary(model)

```


#### Utiliser la fonction CrossTable pour évaluer le modèle :
```{r}
library(rpart)
library(gmodels)
CrossTable(train_data$default, predict(model, train_data), prop.chisq = FALSE, prop.t = FALSE, prop.r = FALSE)
CrossTable(test_data$default, predict(model, test_data), prop.chisq = FALSE, prop.t = FALSE, prop.r = FALSE)

```


